### 2020-07-21 paper/conclusion.tex

The online reprocessing and refueling system is designed to operate as a long-term reactivity control in the MSRs. However, we cannot rely on online reprocessing to adjust reactivity quickly. Additionally, the Nuclear Regulatory Commission (NRC) prescribes that one of two independent reactivity control systems should use control rods. Consequently, we proposed a reactivity control system design based on control rods in addition to the 
online feed system reactivity control in the 
Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR). The 
design has been evaluated at the startup for a full 3D model of the SD-TMSR using the
SERPENT-2 Monte-Carlo code. We considered three startup fuel salt compositions:
(1) $^{232}$Th as fertile and $^{233}$U as fissile material; 
(2) $^{232}$Th and Pu, extracted from \gls{LWR} \gls{SNF}; (3) 
$^{232}$Th and TRU, extracted from \gls{LWR} \gls{SNF}.

@@

In case of malfunction of the other CR clusters (e.g., stuck in the upper 
position), the outer ring of the CSD failed to counteract the excess 
reactivity of the core initially loaded with reactor-grade Pu and TRU elements. Therefore, the fuel salt must be drained into subcritical tanks to shut down the SD-TMSR.
However, the worth of the outer ring of the CSD is sufficient 
to compensate the excess reactivity for the core refueled by $^{233}$U.

>>>>

In the current work, we proposed a first-ever reactivity control system design based on control rods in addition to the 
online feed system reactivity control in the 
Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR). The 
design has been evaluated at the startup for a full 3D model of the SD-TMSR using the
SERPENT-2 Monte-Carlo code. We considered three startup fuel salt compositions:
(1) $^{232}$Th as fertile and $^{233}$U as fissile material; 
(2) $^{232}$Th and Pu, extracted from \gls{LWR} \gls{SNF}; (3) 
$^{232}$Th and TRU, extracted from \gls{LWR} \gls{SNF}.

@@

In case of malfunction of the other CR clusters (e.g., stuck in the upper 
position), the outer ring of the CSD failed to counteract the excess 
reactivity of the core initially loaded with reactor-grade Pu and TRU elements. Therefore, the fuel salt temperature will rise, melt a freeze plug, and hot salt will be drained into subcritical drain tanks to safely shut down the reactor.
However, the worth of the outer ring of the CSD is sufficient 
to compensate the excess reactivity for the core refueled by $^{233}$U.

### 2020-07-21 paper/results.tex

The excess reactivity $\rho$$_e$ is calculated at zero burnup (steady-state 
calculation), when all control rods (CRs) are fully withdrawn. The $\rho_e$ for $^{233}$U, 
reactor-grade Pu, and TRU used as initial fissile material are listed in Table~\ref{tab:excess}.
The previously studied $^{233}$U case \cite{ashraf2020Strategies} recorded the maximum reactivity
during 60 effective full-power years (EFPY) of reactor operation to be 
$4.27\pm0.01$ $\$$ (see Figure~\ref{fig:keff_25} at $\approx$ 8 EFPY).
The proposed reactivity control system must compensate such reactivity at startup and during burnup.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{keff_25.png}
	\vspace{-0.5in}
	\caption{Uncontrolled effective multiplication factor during 60 EFPY of reactor operation including periodic fissile material insertion (confidence interval $\pm\sigma$ is shaded) \cite{ashraf2020whole}.} 
	\label{fig:keff_25}
\end{figure}

\begin{table}  %[!hb]
	\caption{The excess reactivity for the SD-TMSR core with different initial fissile materials.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{3cm} s s s}
		\hline
		Initial fissile materials       				&  $^{233}$U & reactor-grade Pu&  TRU \\
		\hline
		$\rho_e$					& $1.65\pm0.04$ $\$$ & $4.11\pm0.02$ $\$$ & $15.38\pm0.04$ $\$$ \\
		\hline
	\end{tabularx}
	\label{tab:excess}
\end{table}

@@

In case of malfunction of other CR clusters (e.g., stuck in the upper 
position), the outer ring of the CSD will be able to compensate the excess reactivity of the core initially loaded by $^{233}$U.
Meanwhile, it will fail to compensate the excess 
reactivity of the core initially loaded by reactor-grade Pu and TRU elements. In this unlikely case, the fuel salt must be drained into subcritical tanks to shut down the SD-TMSR.

>>>>

The excess reactivity $\rho$$_e$ is calculated at zero burnup (steady-state 
calculation), when all control rods (CRs) are fully withdrawn. The $\rho_e$ for $^{233}$U, 
reactor-grade Pu, and TRU used as initial fissile material are listed in Table~\ref{tab:excess}.
For $^{233}$U case \cite{ashraf2020Strategies} the maximum observed excess reactivity is $4.27\pm0.01$ $\$$ during 60 effective full-power years (EFPY) of operation (see Figure~\ref{fig:keff_25} at $\approx$ 8 EFPY).
The proposed reactivity control system must compensate such reactivity at startup and during burnup.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{keff_25.png}
	\vspace{-0.5in}
	\caption{Uncontrolled effective multiplication factor during 60 EFPY of reactor operation
		including periodic $^{233}$U/$^{232}$Th insertion (confidence interval $\pm\sigma$ is shaded) \cite{ashraf2020whole}.} 
	\label{fig:keff_25}
\end{figure}

\begin{table}  %[!hb]
	\caption{The excess reactivity at startup for the SD-TMSR core with different initial fissile materials.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{3cm} s s s}
		\hline
		Initial fissile materials       				&  $^{233}$U & reactor-grade Pu&  TRU \\
		\hline
		$\rho_e$					& $1.65\pm0.04$ $\$$ & $4.11\pm0.02$ $\$$ & $15.38\pm0.04$ $\$$ \\
		\hline
	\end{tabularx}
	\label{tab:excess}
\end{table}

@@

In case of malfunction of other CR clusters (e.g., stuck in the upper 
position), the outer ring of the CSD will be able to compensate the excess reactivity of the core initially loaded by $^{233}$U.
Meanwhile, it will fail to compensate the excess 
reactivity of the core initially loaded by reactor-grade Pu and TRU elements. In this unlikely case, the fuel salt temperature will rise, melt a freeze plug, and hot salt will be drained into subcritical drain tanks to safely shut down the reactor.
